Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-08 paper/paper.tex
added reminders
added reformulation comment

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target graph. This allows for the development of
    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
    their effectiveness. We are then able to solve this problem on most of the standard problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
    too large for current maximum common subgraph algorithms to handle.
\end{abstract}

\section{Introduction}

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

>>>>

\begin{abstract}
    When a small pattern graph does not occur inside a larger target graph, we can ask how to find
    ``as much of the pattern as possible'' inside the target graph. In general, this is known as the maximum
    common subgraph problem, which is much more computationally challenging in practice than
    subgraph isomorphism. We introduce a restricted alternative, where we ask if all but $k$
    vertices from the pattern can be found in the target graph. This allows for the development of
    slightly weakened forms of certain invariants from subgraph isomorphism which are based upon degree and
    number of paths.  We show that when $k$ is small, weakening the invariants still retains much of
    their effectiveness. We are then able to solve this problem on most of the standard problem
    instances used to benchmark subgraph isomorphism algorithms, despite these instances being much
    too large for current maximum common subgraph algorithms to handle.
\end{abstract}
\todo{try code on MCS instances}
\section{Introduction}
\todo{talk about subgraph isomorphism applications, particularly vision}
\todo{talk about reformulating}
The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.
